The \dealii{} Library, Version 9.4

### 2022-05-03 9.4/paper.tex
Removed value of weight. Not important in this context. (Default value is 1000.)
Adjust indent.
Added bullet-point for pipe_junction.

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class does not output a numerical solution 
  on the cells of the original triangulation, but interpolates the result 
  onto a second triangulation (which can be completely unrelated). 
  By using this class, one can output the result obtained on an 
  unstructured mesh on a structured one, which might be a more
  memory-efficient storage format, or one can create a slice in 3D.
  \item The new function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows to find the MPI
  rank of the subdomain of a distributed mesh that contains a given point.
  It is communication-free and leverages the functionality of p4est (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. Based on the information obtained,
  communication pattern in \texttt{Utilties::MPI::RemotePointEvaluation} can be set up efficiently. Furthermore, this function could be used in the future to allow
  particle simulations where particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
\end{itemize}
%
The changelog lists more than 150 other features and bugfixes.

@@

The 9.4 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_3_0_and_9_4_0.html}
{around 40 incompatible changes}; see \cite{changes94}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority changes internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item In continuation of our attempt to merge the classes \texttt{DoFHandler} and \texttt{hp::DoFHandler}, we have removed the
  template parameter \texttt{DoFHandlerType} from number of classes and
  functions and replaced it by \texttt{dim}/\texttt{spacedim}. Affected
  classes are, e.g., \texttt{SolutionTransfer} and \texttt{DataOut}. 
  \item \texttt{FE\_RaviartThomasNodal} now uses a different polynomial space to allow
for a simpler use for faces in non-standard orientation. The new polynomials
are anisotropic tensor products of Lagrange polynomials on the points of the
Gauss--Lobatto quadrature formula. This change leads to different entries, for example, in
the matrices and constraints, but no change in accuracy should be expected as the resulting polynomial
space spans the same polynomials.
\item We made different changes in the repartitioning of \texttt{parallel::distributed::Triangulation}. Most notably, we have
removed the default weight (10,000) in order to ensure consistency with the rest
of the library.

\end{itemize}

>>>>

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class does not output a numerical solution 
  on the cells of the original triangulation, but interpolates the result 
  onto a second triangulation (which can be completely unrelated). 
  By using this class, one can output the result obtained on an 
  unstructured mesh on a structured one, which might be a more
  memory-efficient storage format, or one can create a slice in 3D.
  \item The new function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows to find the MPI
  rank of the subdomain of a distributed mesh that contains a given point.
  It is communication-free and leverages the functionality of p4est (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. Based on the information obtained,
  communication pattern in \texttt{Utilties::MPI::RemotePointEvaluation} can be set up efficiently. Furthermore, this function could be used in the future to allow
  particle simulations where particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description will be applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \todo[inline]{[MF] If desired, I can extend this part into its own section of the main chapter. With figures, this would probably occupy about 3/4 of a page.}
\end{itemize}
%
The changelog lists more than 150 other features and bugfixes.

@@

The 9.4 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_3_0_and_9_4_0.html}
{around 40 incompatible changes}; see \cite{changes94}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority changes internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item In continuation of our attempt to merge the classes \texttt{DoFHandler} and \texttt{hp::DoFHandler}, we have removed the
  template parameter \texttt{DoFHandlerType} from number of classes and
  functions and replaced it by \texttt{dim}/\texttt{spacedim}. Affected
  classes are, e.g., \texttt{SolutionTransfer} and \texttt{DataOut}. 
  \item \texttt{FE\_RaviartThomasNodal} now uses a different polynomial space to allow
  for a simpler use for faces in non-standard orientation. The new polynomials
  are anisotropic tensor products of Lagrange polynomials on the points of the
  Gauss--Lobatto quadrature formula. This change leads to different entries, for example, in
  the matrices and constraints, but no change in accuracy should be expected as the resulting polynomial
  space spans the same polynomials.
  \item We made different changes in the repartitioning of \texttt{parallel::distributed::Triangulation}.
  Most notably, we have removed the default weight in order to ensure consistency with the rest of the
  library.
\end{itemize}
